The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-06-26 albatros_paper.tex
HCC fixed typo
HCC added disclaimer sentence about LWA antenna at low freqs

\begin{figure}
  \begin{center} \includegraphics[width=1.0\linewidth]{Figures/albatros_2elem_schematic/albatros_2elem_schematic.pdf}
    \caption{Two-element \albatros\ pathfinder block diagram.  Signals
      from two dual-polarzation LWA antennas are amplified by
      front-end active baluns~\citep{2012PASP..124.1090H}.  The
      antennas are connected via 100-m coaxial cables to the back-end
      readout electronics, which are housed in a Faraday cage denoted
      by the dashed box.  Each of the four antenna outputs is passed
      to a second-stage electronics chain consisting of filters and
      further amplfication.  The signals are digitized at 250~Msamp/s
      by a SNAP board, which includes an on-board FPGA that computes
      auto- and cross-spectra from and between the four inputs.  A
      Raspberry Pi controls the SNAP board and saves the data.}
    \label{Fig:albatros2_schem}
  \end{center}
\end{figure}

@@

We employ two dual-polarization Long Wavelength Array (LWA) dipole
antennas~\citep{Memo28}.  The LWA antennas have a long development
history, are well characterized, and are simple to install and
physically robust.  The antennas form an east--west baseline with a
separation of \SI{110}{m}, and the polarizations are aligned with the
cardinal directions.  Welded wire mesh screens, roughly 3~m on a side,
are installed on the ground below the antennas.
% do we want/need to say anything about the omnidirectional primary beam?

>>>>

\begin{figure}
  \begin{center} \includegraphics[width=1.0\linewidth]{Figures/albatros_2elem_schematic/albatros_2elem_schematic.pdf}
    \caption{Two-element \albatros\ pathfinder block diagram.  Signals
      from two dual-polarization LWA antennas are amplified by
      front-end active baluns~\citep{2012PASP..124.1090H}.  The
      antennas are connected via 100-m coaxial cables to the back-end
      readout electronics, which are housed in a Faraday cage denoted
      by the dashed box.  Each of the four antenna outputs is passed
      to a second-stage electronics chain consisting of filters and
      further amplfication.  The signals are digitized at 250~Msamp/s
      by a SNAP board, which includes an on-board FPGA that computes
      auto- and cross-spectra from and between the four inputs.  A
      Raspberry Pi controls the SNAP board and saves the data.}
    \label{Fig:albatros2_schem}
  \end{center}
\end{figure}

@@

We employ two dual-polarization Long Wavelength Array (LWA) dipole
antennas~\citep{Memo28}.  The LWA antennas have a long development
history, are well characterized, and are simple to install and
physically robust.  The antennas form an east--west baseline with a
separation of \SI{110}{m}, and the polarizations are aligned with the
cardinal directions.  Welded wire mesh screens, roughly 3~m on a side,
are installed on the ground below the antennas.  Although the LWA
antenna is not optimized for observations below 10~MHz, using this
standard antenna allowed an initial test of the site and of the
interferometer systems.  For the final \albatros\ array, we are
exploring alternative antenna designs that will that will cover the
full frequency range.

% do we want/need to say anything about the omnidirectional primary beam?
